A Software Engineering Perspective on \\ OpenMP and PThreads

### 2017-08-09 sections/01-introduction.tex
Reviewing Introduction

Programming multi-core architectures demand different skills and tools from
what is needed for traditional sequential programming. Selecting an effective
language, framework or API for parallel and distributed programming is a
challenge for teachers and students, especially due to the quantity and
heterogeneity of available resources.

Tools with a higher level of abstraction may provide a smoother transition from
sequential to parallel and distributed programming, making it easier for
students to develop working code. The cost of high-level abstractions often is
the hiding of underlying concepts, problems and solutions, as well as code
performance.

>>>>

Programming multi-core architectures demand different skills and tools from
what is needed for traditional sequential programming. Selecting an effective
language, framework or API for parallel, and distributed programming is a
challenge for teachers and students, especially due to the quantity and
heterogeneity of available resources.

Tools with a higher level of abstraction may provide a smoother transition from
sequential to parallel and distributed programming, making it easier for
students to develop working code. The cost of high-level abstractions often is
the hiding of underlying concepts, problems, and solutions, as well as code
performance.
